---
title: "Assignment2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Abstruct
What is the research question
Did Abolishment of Apartheid play a significant role in reducing social inequality in South Africa?

Why this research is interesting
1, because this is interesting
2, because data can be easily found
3, because if this assumption can be proven, 

How we prove the assumption
1, Gathering data
  crimerate
    crimerate of whites
    crimerate of black
  level of education
    level of education of white people
    level of education of black people
  level of income
    from wdi data
2, Compare the gaps of those indicators among races between the period of Apartheid and now.

What data we used in this research
1, Crimerate in South Africa
2, level of education
3, level of income

Conclusion
Abolishing Apartheid was extremely effective to reduce social inequality!-I don't think so!!

##data gathering
We use following data sources
  http://www.tradingeconomics.com/
  http://data.worldbank.org/
  
We try to use WDI packages. First, we investigate indicator names by using following code.
```{r}
library(WDI)
WDIsearch('gdp.*capita.*constant')
```



what is the country code of South Africa? see iso2c codes
```{r}
dat = WDI(indicator='NY.GDP.PCAP.KD', country=c('ZA'), start=1960, end=2012)
head(dat)
```


We compare various indicator before and after 1994, the year Apartheid officially abolished.


