---
title: "Assignment2"
output: html_document
bibliography: bibliography.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Research Question 
Our Research Question:
Twenty Years since the end of Apartheid: Did the collapse of Apartheid play a significant role in reducing racial and social inequality in South Africa? Is post-apartheid South Africa better off or worse off than during the aparthed era? 

Why is this research  interesting:
After the collapse of the apartheid, South Africa held its very first historic democratic election in 1994 and announced to the world a new begnning of the country. By electing Nelson Mandel as the president of South Africa, people of all races in the country hoped to see democratic policies which would alleviate poverty and social inequality. Now that over 20 years have passed, the country has been asked for its transition whether or not Mandela's demoratic vision has been fulfilled, especially in terms of non-racial, equal, and progessive political economic development. Our research, therefore, aims to analyze the country's performance in meeting the targets and develivering policies by making comparisons of various social features before and after the Apartheid. This research will be interesting since not only we deal with unique country, South Africa, where experienced very controversial history of racial segregation and white supremach, but also we can evaluate its democratic development and expectation based on several social indicators.     


How we prove the assumption
1, Gathering data
  crimerate
    crimerate of whites
    crimerate of black
  level of education
    level of education of white people
    level of education of black people
  level of income
    from wdi data
2, Compare the gaps of those indicators among races between the period of Apartheid and now.

What data we used in this research
1, Crimerate in South Africa
2, level of education
3, level of income

Conclusion
Abolishing Apartheid was extremely effective to reduce social inequality!-I don't think so!!

##data gathering
We use following data sources
  http://www.tradingeconomics.com/
  http://data.worldbank.org/
  
We try to use WDI packages. First, we investigate indicator names by using following code.
```{r}
library(WDI)
WDIsearch()
WDIsearch('gdp.*capita.*constant')
```



what is the country code of South Africa? see iso2c codes
```{r}
gdp = WDI(indicator='NY.GDP.PCAP.KD', country=c('ZA'), start=1960, end=2012)
trd = WDI(indicator='NE.TRD.GNFS.ZS', country=c('ZA'), start=1960, end=2012)

```

plot the gdp and trade
```{r}
library(ggplot2)
ggplot(gdp, aes(year, NY.GDP.PCAP.KD, color=country)) + geom_line() +  xlab('Year') + ylab('GDP per capita')
ggplot(trd, aes(year, NE.TRD.GNFS.ZS, color=country)) + geom_line() +  xlab('Year') + ylab('Trade (% of gdp)')
```

calculate the trade amount
```{r}
realtrd = gdp * trd
ggplot(realtrd)

```


We compare various indicator before and after 1994, the year Apartheid officially abolished.

